\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2016-12-14 report/paper.tex
navier-stokes equations

\usepackage{bm}
\newcommand{\vect}[1]{\bm{#1}} % bold vector

@@

\section{Introduction}
    %explain the context of the work:
	%What exactly is the problem?
	%What have you created?
    Smoothed particle hydrodynamics, \textit{SPH}, is a method that was first implemented in 1977 for astrophysical simulations by Gingold et al.~\cite{firstSPH}.
    Since then SPH has become a popular method for complex fluid simulations.
    SPH is a mesh-free Lagrangian method where the fluid is split into discrete sets defined as particles, which move in space and change physical properties as time progresses.
    % More about Lagrangian and maybe navier stokes?

    % We used this article
    In this paper we are going to introduce the results from reproducing the divergence-free smoothed particle hydrodynamics method presented by Bender et al.~\cite{bender}.
    It is a method which corrects the divergence error, aiming for a divergence-free velocity field which is needed for an incompressible fluid.
    For the solution to be divergence-free the density has to be constant over time.

@@

    \begin{equation} \label{eq:gradKernel}
        \partial W_h(q(x)) =  x \cdot \frac{1}{h \left \| x \right \|} \cdot \frac{1}{\pi h^3} \left\{\begin{matrix}
        - 3q + \frac{9}{4}q^2 & 0 \leqslant q < 1 \\ 
        \\
        - \frac{3}{4}(2-q)^2 & 1 \leqslant q < 2\\ 
        \\
        0 & q \geqslant 2
      \end{matrix}\right.
    \end{equation}
    % maybe specify x here as well

@@

@@

\subsection{Navier-stokes}
% Write about non pressure forces, velocity osv..?
\subsection{Adapted time step}

% CFL condition, explain why its necessary and how its assured that each rendered frame has the same time step.
In order to assure a stable simulation it is necessary to adapt the time step depending on the motion. 
The quicker the particles move the smaller time steps are taken such that the numerical 
error of the explicit time integration is negligible. For this is a condition proposed by Courant–Friedrichs–Lewy used often refered as the CFL-condition show in equation \ref{eq:cfl}. The time step $\Delta t$ is equal to a fraction of the particle's diameter $d$ divided by the maximum velocity $\vect{V_{max}}$ in the scene.

\begin{equation}\label{eq:cfl}
\Delta t \leq \frac{0.4 \cdot d}{\vect{V_{max}}}
\end{equation}

Each rendered frame however have a constant time step in order to ensure no speed change in the playback of the rendered video. This is decided from the user side as a desired fps parameter. This means that the simulation loop can iterate multiple times within each frame adaptively depending on the maximum velocity.

\subsection{Density and alpha factors}
\subsection{Screen space fluid rendering}

>>>>

@@

\section{Introduction}
    %explain the context of the work:
	%What exactly is the problem?
	%What have you created?
    Smoothed particle hydrodynamics, \textit{SPH}, is a method that was first implemented in 1977 for astrophysical simulations by Gingold et al.~\cite{firstSPH}.
    Since then SPH has become a popular method for complex water simulations.
    SPH is a mesh-free Lagrangian method where the particles move in space and change physical properties as time progresses.
    % More about Lagrangian and maybe navier stokes?

    % We used this article
    In this paper we are going to introduce the results from reproducing the divergence-free smoothed particle hydrodynamics method introduced by Bender et al.~\cite{bender}.
    It is a method which corrects the divergence error, aiming for a divergence-free velocity field which is needed for an incompressible fluid.
    For the solution to be divergence-free the density has to be constant over time.

@@

    \begin{multline} \label{eq:gradKernel}
        \partial W_h(q(x)) = \\ x \cdot \frac{1}{h \left \| x \right \|} \cdot \frac{1}{\pi h^3} \left\{\begin{matrix}
        - 3q + \frac{9}{4}q^2 & 0 \leqslant q < 1 \\ 
        \\
        - \frac{3}{4}(2-q)^2 & 1 \leqslant q < 2\\ 
        \\
        0 & q \geqslant 2
      \end{matrix}\right.
    \end{multline}
    % maybe specify x here as well

@@

\subsection{Navier-Stokes}
    Navier-Stokes equations describes incompressible fluids and is therefore suitable for SPH simulations. The equations expressed in Lagrangian coordinates can be found in Equation~\ref{eq:nsDensity} and~\ref{eq:nsVelocity}.

    \begin{equation} \label{eq:nsDensity}
        \frac{D\rho}{Dt} = 0 \Leftrightarrow \bigtriangledown \cdot \textbf{v} = 0 
    \end{equation}

    \begin{equation} \label{eq:nsVelocity}
        \frac{D\textbf{v}}{Dt} = \frac{1}{\rho} \bigtriangledown p + v \bigtriangledown ^2 \textbf{v} + \frac{\textbf{f}}{\rho}
    \end{equation}

    In the equations $\frac{D\rho}{Dt}$ and $\frac{D\textbf{v}}{Dt}$ denotes the derivate of the density $\rho$ and the velocity $\textbf{v}$ respectively. The pressure, kinematic viscosity and body forces are denoted by $p,v$ and $\textbf{f}$ respectively. Due to the incompressibility, the partial derivate of the density with respect to the time is zero which implies the equivalence of the equations in~\ref{eq:nsDensity} where the second part $\bigtriangledown \cdot \textbf{v} = 0$ induce that the field is free from divergence.

@@

% Write about non pressure forces, velocity osv..?
\subsection{Adapted time step}
\subsection{Density and alpha factors}
\subsection{Screen space fluid rendering}
